\SW: II. New lens candidates from the CFHTLS discovered through citizen science

### 2015-04-12 doc/sw-cfhtls.tex
read through all sections

With the cross-section, and the luminosity functions specified, we
calculate the expected number of sources behind a candidate lensing
galaxy using Eq.~\ref{eqn:nsrc}. We need to generate a large number of
simulated lenses (larger than the number of real galaxy lenses we expect
to find in \cfhtls) in order to have a reasonably large and diverse
training sample for thousands of \sw volunteers. Therefore, we
artificially boost the average number of sources by a factor (see
Table~\ref{tab:thresh}, which increases the occurrence of lensing. We
draw a Poisson deviate, $N_{\rm src}$ with a mean equal to the boosted
average number of sources. If $N_{\rm src}$ is greater than zero, then
this galaxy is flagged as a potential lensing galaxy.

@@

We calculate the luminosity and velocity dispersion for the BGG and each of the
member galaxies following the same prescription as in
\Sref{sect:gallens}. To calculate the average number of sources that get
lensed by such a system, we need to calculate the lensing cross-section for each
of these potential lensing groups. The complexity in the lens models makes it
analytically intractable to calculate the size of the caustics\footnote{The lens
mass distribution determines size and shape of the caustics. Any source
located within the caustics will form multiple lensed images which is the
criteria for strong lensing. To further understand caustics, see XXX.}.
Therefore, we generate the caustics numerically using \gravlens and then
determine the area covered by the caustics. We consider only galaxies as our
background source population since group or cluster-scale quasar lenses are
expected to be extremely rare in the \cfhtls.  Following the same procedure
as described in \Sref{sect:gallens}, we calculate the number of galaxies
expected to lie behind every potential lensing group (see Eq.~\ref{eqn:nsrc}).
As before, for each background galaxy within the lens cross-section, a redshift
and an $i$-band magnitude is determined by drawing galaxies randomly from the
respective distributions (see Eqs.~\ref{eqn:ps}-\ref{eqn:ns}).

All those groups that are found to have no background galaxies within the
cross-sectional area are rejected and the rest are included as potential lenses.
As mentioned earlier, we artificially boost the total number of sources behind
every lens but ensure that (check XXX) the statistical properties such as the profile of the
image separation distribution are not affected (see \Fref{fig:remudist}). We
follow the same procedure and apply thresholds to determine properties
of the lensed galaxies for every lens as are described for galaxy-galaxy lenses
in the previous section. The thresholds are same as those used for
galaxy lenses (see \Tref{tab:thresh}) and are reported within ``()'', if
different for group-scales. The simulated lensed images are then added
to the real \cfhtls~images with the BGGs as the center by following
exactly the same procedure as described in the previous section.

@@

In this section, we describe the \sw-\cfhtls lens sample (henceforth,
called the \sw lens sample). We find a total of  (and XXX new)
candidates with averaged grade $0<$G$<1.3$ (low probability sample)
which means - in the worst case, at least one of the inspector thought
the candidate is possibly a lens and in the best case, all three
inspectors thought the candidate is possibly a lens (that is,
a grade of 1)\footnote{If grades from the inspectors were found to be discrepant
by 2 or more, these were discussed and re-graded to resolve the
discrepancy.}. Further information on the low probability sample such as
their positions and images is available at
http://spacewarps.org/\#/projects/CFHTLS/. Note that if all of the inspectors gave
a grade of 0 to a candidate, then it is discarded from the sample.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_rein.pdf}
\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_mag.pdf}
\caption{ \label{fig:stackremg}
Candidate detections by the \rf, \sw and the \af as a
function of the Einstein radius and $g$ band magnitude of the lensed
images.
%(XXXX check how different are the estimates from the different measurement techniques for a given lens candidates.)
}
\end{center}
\end{figure*}

>>>>

With the cross-section, and the luminosity functions specified, we
calculate the expected number of sources behind a candidate lensing
galaxy using Eq.~\ref{eqn:nsrc}. We need to generate a large number of
simulated lenses (larger than the number of real galaxy lenses we expect
to find in \cfhtls) in order to have a reasonably large and diverse
training sample for thousands of \sw volunteers. Therefore, we
artificially boost the average number of sources by a factor (see
Table~\ref{tab:thresh}), which increases the occurrence of lensing. We
draw a Poisson deviate, $N_{\rm src}$ with a mean equal to the boosted
average number of sources. If $N_{\rm src}$ is greater than zero, then
this galaxy is flagged as a potential lensing galaxy.

@@

We calculate the luminosity and velocity dispersion for the BGG and each of the
member galaxies following the same prescription as in
\Sref{sect:gallens}. To calculate the average number of sources that get
lensed by such a system, we need to calculate the lensing cross-section for each
of these potential lensing groups. The complexity in the lens models makes it
analytically intractable to calculate the size of the caustics\footnote{The lens
mass distribution determines size and shape of the caustics. Any source
located within the caustics will form multiple lensed images which is the
criteria for strong lensing. To further understand caustics, see e.g., \citet{Schneider1992}.}.
Therefore, we generate the caustics numerically using \gravlens and then
determine the area covered by the caustics. We consider only galaxies as our
background source population since group or cluster-scale quasar lenses are
expected to be extremely rare in the \cfhtls.  Following the same procedure
as described in \Sref{sect:gallens}, we calculate the number of galaxies
expected to lie behind every potential lensing group (see Eq.~\ref{eqn:nsrc}).
As before, for each background galaxy within the lens cross-section, a redshift
and an $i$-band magnitude is determined by drawing galaxies randomly from the
respective distributions (see Eqs.~\ref{eqn:ps}-\ref{eqn:ns}).

All those groups that are found to have no background galaxies within the
cross-sectional area are rejected and the rest are included as potential lenses.
As mentioned earlier, we artificially boost the total number of sources behind
every lens but ensure that the statistical properties such as the profile of the
image separation distribution are not affected (see \Fref{fig:remudist}). We
follow the same procedure and apply thresholds to determine properties
of the lensed galaxies for every lens as are described for galaxy-galaxy lenses
in the previous section. The thresholds are same as those used for
galaxy lenses (see \Tref{tab:thresh}) and are reported within ``()'', if
different for group-scales. The simulated lensed images are then added
to the real \cfhtls~images with the BGGs as the center by following
exactly the same procedure as described in the previous section.

@@

In this section, we describe the \sw-\cfhtls lens sample (henceforth,
called the \sw lens sample). We find a total of XXX (and XXX new)
candidates with averaged grade $0<$G$<1.3$ (low probability sample)
which means - in the worst case, at least one of the inspector thought
the candidate is possibly a lens and in the best case, all three
inspectors thought the candidate is possibly a lens (that is,
a grade of 1)\footnote{If grades from the inspectors were found to be discrepant
by 2 or more, these were discussed and re-graded to resolve the
discrepancy.}. Further information on the low probability sample such as
their positions and images is available at
http://spacewarps.org/\#/projects/CFHTLS/. Note that if all of the inspectors gave
a grade of 0 to a candidate, then it is discarded from the sample.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_rein.pdf}
\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_mag.pdf}
\caption{ \label{fig:stackremg}
Candidate detections by the \rf, \sw and the \af as a
function of the Einstein radius and $g$ band magnitude of the lensed
images.
%{\bf check how different are the estimates from the different
%measurement techniques for a given lens candidates.}
}
\end{center}
\end{figure*}
